Mechanization of Separation in Generic Extensions

### 2019-01-06 LICS/zfc-axioms.tex
eds varias
Enumeración de los esquemas

The axioms of Zermelo and Fraenkel ($\ZF$) form a
countably infinite list of first-order sentences in a language
consisting of an only binary relation symbol $\in$. These include the
axioms of Extensionality, Pairing, Union, Powerset, Foundation, Infinity, and two
axiom-schemes collectively referred to as Axiom of Separation:
\emph{For every $A$, $a_1,\dots,a_n$,  and  a formula
  $\psi(x_0,x_1,\dots,x_n)$, there exists $\{a\in  A:
  \psi(a,a_1,\dots,a_n)\}$}, 
and Axiom of Replacement: \emph{For every $A$, $a_1,\dots,a_n$,  and
  a formula   $\psi(x,z,x_1\dots,x_n)$, if 
  $\forall x.\exists!z.\psi(x,z,x_1,\dots,x_n)$,  there exists 
  $\{b : \exists a\in A. \psi(a,b,a_1,\dots,a_n)\}$}.
An excellent introduction to the axioms and the motivation behind them
can be found in Shoenfield \cite{MR3727410}.

@@

above $\psi$), where \isatt{sats\,::\,"[i,i,i]=>o"} is the satisfaction
relation between a set model with an environment and an internalized
formula. Thanks to Pairing, these 

>>>>

The axioms of Zermelo and Fraenkel ($\ZF$) form a
countably infinite list of first-order sentences in a language
consisting of an only binary relation symbol $\in$. These include the
axioms of Extensionality, Pairing, Union, Powerset, Foundation, Infinity, and two
axiom-schemes collectively referred as
\begin{inlinelist}[label=(\emph{\alph*})]
\item Axiom of Separation:
\emph{For every $A$, $a_1,\dots,a_n$,  and  a formula
  $\psi(x_0,x_1,\dots,x_n)$, there exists $\{a\in  A:
  \psi(a,a_1,\dots,a_n)\}$}, 
and \item Axiom of Replacement: \emph{For every $A$, $a_1,\dots,a_n$,  and
  a formula   $\psi(x,z,x_1\dots,x_n)$, if 
  $\forall x.\exists!z.\psi(x,z,x_1,\dots,x_n)$,  there exists 
  $\{b : \exists a\in A. \psi(a,b,a_1,\dots,a_n)\}$}.
\end{inlinelist}
An excellent introduction to the axioms and the motivation behind them
can be found in Shoenfield \cite{MR3727410}.

@@

above $\psi$). Thanks to Pairing, these 
